MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd
cn uptake for own use

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) # remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

##2. For Grassland
#leaf c/n model. median = 18. 
#root c/n model median = 41.
#see line 887-888 in Forest_site_org, all derived from "TianDi Grassland", but its BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)
```

@@

## Read data
```{r}
#trendy
#model output
#CABLE-POP
CABLE_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CABLE-POP_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
CABLE_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CABLE-POP_S2_npp_ANN_mean.nc"), varnam = "npp"))

@@

```{r}
#all_maps
not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.79) 
#grassland nue:
(16.37/0.34)
#total nue:
(72.06/1.13) 
#forest nue uncertainty:
(55.74/0.79) * sqrt( (10.62/55.74)^2 +(0.23/0.79)^2)
#grassland nue uncertainty:
(16.37/0.34) * sqrt( (9.65/16.37)^2 +(0.15/0.34)^2)
#pft
(72.06/1.13) * sqrt( (14.35/72.06)^2 +(0.27/1.13)^2)
```

>>>>

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) # remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
#library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

##2. For Grassland
#leaf c/n model. median = 18. 
#root c/n model median = 41.
#see line 887-888 in Forest_site_org, all derived from "TianDi Grassland", but its BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland")  ,by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)
```

@@

## Read data
```{r warning=FALSE}
#trendy
#model output
#CABLE-POP
CABLE_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CABLE-POP_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
CABLE_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CABLE-POP_S2_npp_ANN_mean.nc"), varnam = "npp"))

@@

```{r warning=FALSE}
#all_maps
not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.79) 
#grassland nue:
(16.37/0.34)
#total nue:
(72.06/1.13) 
#forest nue uncertainty:
(55.74/0.79) * sqrt( (10.62/55.74)^2 +(0.23/0.79)^2)
#grassland nue uncertainty:
(16.32/0.34) * sqrt( (9.65/16.32)^2 +(0.15/0.34)^2)
#pft
(72.06/1.13) * sqrt( (14.35/72.06)^2 +(0.27/1.13)^2)
```
